Simulating High-Dimensional Multivariate Data

### 2021-01-21 030-bigsimr-package.Rmd
Update code to bigsimr_0.9.3
2nd draft. Insert Tom / Ania bivariate example

## Basic use illustrated through a minimal example

@@

```{r ch030-margins-alist, echo=TRUE}
margins <- alist(
    qnorm(mean = 77.871, sd = 9.4855),
    qlnorm(meanlog = 3.419, sdlog = 0.6967),
)
```

@@

```{r ch030-margins-mlist, echo=TRUE}
margins <- mlist(
  qnorm(mean = mean(df$Temp), sd = sd(df$Temp)),
  qlnorm(meanlog = mle_mean(df$Ozone), sdlog = mle_sd(df$Ozone))
)
margins
```

@@

We note that the bounds on the Pearson correlation coefficient $R_P$ between these margins is restricted as seen below:

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, method = 'pearson', reps = 1e6)

@@

```{r ch030-sim-margins, echo=TRUE}
x <- rvec(10000, rho, margins)
df_sim <- as.data.frame(x)
colnames(df_sim) <- colnames(df)
```

>>>>

## Bivariate example of basic use

@@

```{r ch030-margins-alist, echo=TRUE, cache=T}
margins <- alist(
    qnorm(mean = 77.871, sd = 9.4855),
    qlnorm(meanlog = 3.419, sdlog = 0.6967)
)
```

@@

```{r ch030-margins-mlist, echo=TRUE}
mlist(
  qnorm(mean = mean(df$Temp), sd = sd(df$Temp)),
  qlnorm(meanlog = mle_mean(df$Ozone), sdlog = mle_sd(df$Ozone))
)
```

@@

The bounds on the Pearson correlation coefficient $R_P$ between these margins is restricted as seen below in our MC estimated correlation bounds:

```{r ch030-cor-bounds-pearson, echo=TRUE}
cor_bounds(margins = margins, method = 'pearson', reps = 1e6)
```

Our MC estimate of the bounds slightly underestimates the theoretic bounds of $(-0.881, 0.881)$. An analytic derivation is presented as an Appendix.

@@

```{r ch030-sim-margins, echo=TRUE}
x <- rvec(10000, R_X, margins)
df_sim <- as.data.frame(x)
colnames(df_sim) <- colnames(df)
```
